A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-06 paper.tex
2d N=(4,4) and (8,8)

\begin{table}[!ht]
 \centering
 \begin{tabular}{c|c|c|c}
 $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{6}*{$(4,4)$} & \multirow{2}*{\hyperref[sect:2d44minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$} & \\ \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d44Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$} & \\  \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d44Atwist] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{dR}})$} & \\  \hline
 \multirow{6}*{$(2,2)$} & \multirow{2}*{\hyperref[sect:2d22minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$} & \\  \cline{2-4}
  & \multirow{2}*{\hyperref[sect:2d22Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to $R$ matter} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, (R/\gg))$} & \\  \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d22Atwist] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{dR}})$} & \\  \hline
 \multirow{2}*{$(0,\mc N_-)$} & \multirow{2}*{\hyperref[sect:2d0Nminimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $\mc N_- - 2$ free fermions} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, (\gg \otimes \CC^{\mc N_- -2})/\gg)$} & \\  \hline
 \multirow{2}*{$(0,4)$} & \multirow{2}*{\hyperref[sect:2d04minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, U \ham \gg)$} & \\  \hline
 \multirow{2}*{$(0,2)$} & \multirow{2}*{\hyperref[sect:2d02minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, R/\gg)$} & \\ \hline
 \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories in two dimensions with gauge group $G$.  When $\mc N=(0,2)$ and $(2,2)$ the theory includes a chiral multiplet valued in a representation $R$. When $\mc N=(0,4)$ and $(4,4)$ the theory includes a hypermultiplet valued in a symplectic representation $U$.}
 \label{table_of_twists_2d}
\end{table}

@@

\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with Matter} \label{sect:2d(2,2)}
First, let's consider the $\mc N=(2,2)$ super Yang-Mills theory, which arises via dimensional reduction from 3d $\mc N=2$ super Yang-Mills.  This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.  The R-symmetry group is $G_R = \spin(2;\CC) \times \spin(2;\CC) \iso \CC^\times \times \CC^\times$, with the factors acting by their vector representation on $W_+$ and $W_-$ repectively.

@@

In the $\mc N=(2,2)$ supersymmetry algebra there is are three classes of non-trivial orbits of square-zero supercharges.  
\begin{itemize}
 \item Square-zero supercharges of rank $(1,0)$ or $(0,1)$, which are holomorphic.  There is a compatible twisting homomorphism from $\mr U(1)$, and a compatible twisting datum $\alpha \colon \mr U(1) \to \spin(2;\RR)$ acting with weight $1$ on $S_+$ and weight $-1$ acting on $S_-$.  
 \item Square-zero supercharges of rank $(1,1)$ are topological, and split into four orbits under the action of $\spin(2;\CC) \times G_R$.  Indeed, we can identify a square-zero supercharge of rank $(1,1)$ as a pair of vectors $((\lambda, \pm i \lambda), (\mu, \pm i \mu)) \in W_+ \oplus W_-$ with $\lambda, \mu \ne 0$.  By acting by $G_R$ we can set $\lambda = \mu = 1$, leaving four orbits, represented by the supercharges $Q_A = ((1,i),(1,i)), Q_A^\dagger = ((1,-i),(1,-i)), Q_B = ((1,i),(1,-i))$ and $Q_B^\dagger = ((1,-i),(1,i))$.  The two A-supercharges are compatible with the A-twisting homomorphism $\phi_{A} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$, and the two B-supercharges are compatible with the B-twisting homomorphism $\phi_{B} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,-1)$.  Moreover, the A-supercharges can be promoted to twisting data using the homomorphism $\alpha_A = \phi_B$, and the B-supercharges can be promoted to twisting data using $\alpha_B = \phi_A$.
\end{itemize}

@@

\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} and \texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with matter} \label{sect:2d(4,4)}
We can likewise consider $\mc N=(4,4)$ super Yang-Mills theory with gauge group $G$, with a hypermultiplet valued in a symplectic representation $U$, by dimensionally reducing 3d $\mc N=4$ super Yang-Mills, or we can consider $\mc N=(8,8)$ super Yang-Mills with gauge group $G$, by dimensionally reducing 3d $\mc N=8$ super Yang-Mills.  We will address these two theories together, since in neither case are there any new classes of twist which were not visible already in the $\mc N=(2,2)$ section above.  In other words, every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.

The R-symmetry group in the $\mc N=(4,4)$ case is $\spin(4;\CC) \times \spin(4;\CC)$, and in the $\mc N=(8,8)$ case it is $\spin(8;\CC)$ (acting on both $W_+$ and $W_-$ by its defining representation.  In this latter case we must be somewhat careful since the $B$-twisting homomorphism $\phi_B$ does not factor through the diagonal.  We may instead compose the inclusion $\spin(2;\CC) \to \spin(3;\CC)$ with the twisting homomorphism from Section \ref{3d8section}.

The following equivalences follow from the results in the previous section by substituting $R = U \oplus \gg$.

\subsubsection{Minimal Twist} \label{sect:2d44minimaltwist}
\begin{theorem}
The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$.  If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with  $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Dol}})$.  This equivalence is $\mr U(1)$-invariant.
\end{theorem}

\subsubsection{Topological A Twist} \label{sect:2d44Atwist}
\begin{theorem}
The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ admits a one-parameter deformation to the A-twist.  This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Hod}})$.  If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with  $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Hod}})$.  This equivalence is $\mr U(1)$-invariant.
\end{theorem}

\subsubsection{Topological B Twist} \label{sect:2d44Btwist}

For the topological B-twist, the following result follows again by substituting $R = U \oplus \gg$, but in order to obtain $\mr U(1)$-equivariance in the $\mc N=(8,8)$ case \chris{...}

\begin{theorem}
The B-twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$.  If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, T^*[2](\gg/\gg))$.  This equivalence is $\mr U(1)$-invariant.
\end{theorem}

>>>>

\begin{table}[!ht]
 \centering
 \begin{tabular}{c|c|c|c}
 $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{6}*{$(4,4)$} & \multirow{2}*{\hyperref[sect:2d44minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$} & \\ \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d44Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$} & \\  \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d44Atwist] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{dR}})$} & \\  \hline
 \multirow{6}*{$(2,2)$} & \multirow{2}*{\hyperref[sect:2d22minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$} & \\  \cline{2-4}
  & \multirow{2}*{\hyperref[sect:2d22Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to $R$ matter} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, (R/\gg))$} & \\  \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d22Atwist] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{dR}})$} & \\  \hline
 \multirow{2}*{$(0,\mc N_-)$} & \multirow{2}*{\hyperref[sect:2d0Nminimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $\mc N_- - 2$ free fermions} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, (\gg \otimes \CC^{\mc N_- -2})/\gg)$} & \\  \hline
 \multirow{2}*{$(0,4)$} & \multirow{2}*{\hyperref[sect:2d04minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, U \ham \gg)$} & \\  \hline
 \multirow{2}*{$(0,2)$} & \multirow{2}*{\hyperref[sect:2d02minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, R/\gg)$} & \\ \hline
 \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories in two dimensions with gauge group $G$.  When $\mc N=(0,2)$ and $(2,2)$ the theory includes a chiral multiplet valued in a representation $R$. When $\mc N=(0,4)$ and $(4,4)$ the theory includes a hypermultiplet valued in a symplectic representation $U$.  We can promote the supersymmetry to $\mc N=(8,8)$ when $U = T^*\gg$, but no new twists occur.}
 \label{table_of_twists_2d}
\end{table}

@@

\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with Matter} \label{sect:2d(2,2)}
First, let's consider the $\mc N=(2,2)$ super Yang-Mills theory, which arises via dimensional reduction from 3d $\mc N=2$ super Yang-Mills.  This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.  The R-symmetry group is $G_R = \ZZ/2\ZZ \ltimes (\spin(2;\CC) \times \spin(2;\CC)) \iso \CC^\times \times \CC^\times$, with the factors acting by their vector representation on $W_+$ and $W_-$ repectively, and with $\ZZ/2\ZZ$ acting on both $W_+$ and $W_-$ by $(a,b) \mapsto (a^{-1}, b^{-1})$.

@@

In the $\mc N=(2,2)$ supersymmetry algebra there is are three classes of non-trivial orbits of square-zero supercharges.  
\begin{itemize}
 \item Square-zero supercharges of rank $(1,0)$ or $(0,1)$, which are holomorphic.  There is a compatible twisting homomorphism from $\mr U(1)$, and a compatible twisting datum $\alpha \colon \mr U(1) \to \spin(2;\RR)$ acting with weight $1$ on $S_+$ and weight $-1$ acting on $S_-$.  
 \item Square-zero supercharges of rank $(1,1)$ are topological, and split into four orbits under the action of $\spin(2;\CC) \times (\CC^\times \times \CC^\times)$.  Indeed, we can identify a square-zero supercharge of rank $(1,1)$ as a pair of vectors $((\lambda, \pm i \lambda), (\mu, \pm i \mu)) \in W_+ \oplus W_-$ with $\lambda, \mu \ne 0$.  By acting by $G_R$ we can set $\lambda = \mu = 1$, leaving four orbits, represented by the supercharges $Q_A = ((1,i),(1,i)), Q_A^\dagger = ((1,-i),(1,-i)), Q_B = ((1,i),(1,-i))$ and $Q_B^\dagger = ((1,-i),(1,i))$.  The $\ZZ/2\ZZ$-action swaps the two A supercharges and the two B supercharges, leaving two orbits under $\spin(2;\CC) \times G_R$.  The A-supercharges are compatible with the A-twisting homomorphism $\phi_{A} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$, and the B-supercharges are compatible with the B-twisting homomorphism $\phi_{B} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,-1)$.  Moreover, the A-supercharges can be promoted to twisting data using the homomorphism $\alpha_A = \phi_B$, and the B-supercharges can be promoted to twisting data using $\alpha_B = \phi_A$.
\end{itemize}

@@

\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} Super Yang-Mills with Matter} \label{sect:2d(4,4)}
We can likewise consider $\mc N=(4,4)$ super Yang-Mills theory with gauge group $G$, with a hypermultiplet valued in a symplectic representation $U$, by dimensionally reducing 3d $\mc N=4$ super Yang-Mills.  No new twists arise, i.e. every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.

The R-symmetry group in the $\mc N=(4,4)$ case is $G_R = \SU(2) \times \spin(4;\CC)$, where $\spin(4;\CC)$ acts on $S_+ \otimes W_+ \oplus S_- \otimes W_- \iso S_+^6 \otimes W_+^6$ -- where $W_+^6$ is the 6d $\mc N=(1,0)$ auxiliary space -- by its fundamental representation on both $W_+$ and $W_-$, and where $\SU(2)$ acts by permuting the two factors, i.e. by its fundamental representation on $W^6$.

In addition to rank $(1,0)$ supercharges, which are holomorphic, there are square-zero rank $(1,1)$ supercharges.  As in Section \ref{sect:2d(2,2)}, these supercharges split into two orbits.

\begin{prop}
There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(4,4)$ supersymmetry algebra, which we will refer to as the A- and B-supercharges.  The B-supercharge occurs as a degeneration of A-type supercharges.
\end{prop}

\begin{proof}
First, let us decompose the 6d semispinor representation $S_+^6$ into $S_+^4 \oplus S_-^4$ as a representation of $\spin(4;\CC)$. A rank $(1,1)$ square-zero supercharge can be identified with the data of a null vector in $S_+^4$, a null vector in $S_-^4$ and a pair of null vectors in $W_+^6$, all non-zero.  There are only two $G_R$-orbits in this space of quadruples of null vectors: either the two null vectors in $W_+^6$ are colinear, or they are distinct.  We will refer to these as the B- and A-supercharges respectively.
\end{proof}

Upon dimensional reduction from 3d $\mc N=4$, the B-supercharge reduced to the 2d $\mc N=(4,4)$ B-supercharge.  Indeed, the 3d B-supercharge squares to zero as an element of the 6d $\mc N=(1,0)$ supersymmetry algebra, which means that in this 6d algebra it has rank 1.  Therefore the two vectors in $W_+^6$ discussed above must be colinear.

\subsubsection{Minimal Twist} \label{sect:2d44minimaltwist}
We obtain the following from the 3d $\mc N=4$ minimal twist of Theorem \ref{3d_4_minimal_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.

\begin{theorem}
The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$. This equivalence is $\mr U(1)$-invariant.
\end{theorem}

\subsubsection{Topological A Twist} \label{sect:2d44Atwist}
We likewise obtain the following from the 3d $\mc N=4$ A-twist of Theorem \ref{3d_4_A_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.

\begin{theorem}
The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ admits a one-parameter deformation to the A-twist.  This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Hod}})$.   This equivalence is $\mr U(1)$-invariant.
\end{theorem}

\subsubsection{Topological B Twist} \label{sect:2d44Btwist}
Finally, we obtain the following from the 3d $\mc N=4$ A-twist of Theorem \ref{3d_4_B_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.

\begin{theorem}
The B-twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$.  This equivalence is $\mr U(1)$-invariant.
\end{theorem}

\subsection{\texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with Matter} \label{sect:2d(8,8)}
Now, let us consider $\mc N=(8,8)$ super Yang-Mills theory by dimensionally reducing 3d $\mc N=8$ super Yang-Mills, or we can consider $\mc N=(8,8)$ super Yang-Mills.  No new twists arise, i.e. every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.

The R-symmetry group in the $\mc N=(4,4)$ case is $G_R = \spin(8;\CC)$, acting on $W_+$ and $W_-$ by its two semispin representations.  As in the $\mc N=(4,4)$ case, the classification of square-zero supercharge is identical to the classification we say in the $\mc N=(4,4)$ case.  Rank $(1,0)$ square zero supercharges, and rank $(1,1)$ square zero supercharges split into two orbits in the following way.

\begin{prop}
There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(8,8)$ supersymmetry algebra, which we will refer to as the A- and B-supercharges.  The B-supercharge occurs as a degeneration of A-type supercharges.
\end{prop}

\begin{proof}
Our aim is to understand the classification of $\spin(8;\CC)$-orbits in the space of pairs of non-zero null-vectors $w_+ \in W_+$ and $w_- \in W_-$.  Since $\spin(8;\CC)$ acts transitively on the possible choices of $w_+$, it remains for us to understand the action of the stabilizer $\stab(w_+) \sub \spin(8;\CC)$ on the space of null vectors $w_-$.  The element $w_+$ is equivalent to the data of a Lagrangian subspace $L \sub V_8$, along with a half-density.  As a representation of the subgroup $\mr{ML}(L)$ of $\stab(w_+)$, the two semispin representations decompose as
\begin{align*}
 W_+ &\iso (\CC \oplus \wedge^2 L \oplus \wedge^4 L) \otimes \det(L)^{-1/2} \\
 W_- &\iso (L \oplus \wedge^3 L) \otimes \det(L)^{-1/2},
\end{align*}
with $w_+ \in \wedge^4 L$.  With respect to this decomposition, say $w_- = (v_1,v_3)$.  If $v_1 \ne 0$, then we can act by $\wedge^2 L \sub \stab(w_+)$ to make $v_3 = 0$.  Under the action of $\SL(L)$ all such non-zero $v_1$ are in the same orbit.  Likewise if $v_1 = 0$ then $v_3 \ne 0$ and we can act by $\SL(L)$ to see that all such non-zero $v_3$ are in the same orbit.  There are, therefore, two orbits once again, with one degenerating to the other.
\end{proof}

Upon dimensional reduction from 3d $\mc N=8$, the B-supercharge reduces to the 2d $\mc N=(8,8)$ B-supercharge.  Indeed, if we forget down to $\mc N=4$ supersymmetry, then the B-twist should correspond to the B-twist.  In both $\mc N=(4,4)$ and $\mc N=(8,8)$ the two orbits are distinguished, in that the orbit of B-twists lies in the closure of the orbit of A-twists.

\subsubsection{Minimal Twist} \label{sect:2d88minimaltwist}
We obtain the following from the 3d $\mc N=8$ minimal twist of Theorem \ref{3d_8_minimal_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.

\begin{theorem}
The holomorphic twist of 2d $\mc N=(8,8)$ super Yang-Mills is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Dol}})$. This equivalence is $\mr U(1)$-invariant.
\end{theorem}

\subsubsection{Topological A Twist} \label{sect:2d88Atwist}
We obtain the following from the 3d $\mc N=8$ A-twist of Theorem \ref{3d_8_A_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.

\begin{theorem}
The holomorphic twist of 2d $\mc N=(8,8)$ super Yang-Mills admits a one-parameter deformation to the A-twist.  This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Hod}})$.   This equivalence is $\mr U(1)$-invariant.
\end{theorem}

\subsubsection{Topological B Twist} \label{sect:2d88Btwist}
We obtain the following from the 3d $\mc N=8$ A-twist of Theorem \ref{3d_8_B_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.

\begin{theorem}
The B-twist of 2d $\mc N=(8,8)$ super Yang-Mills is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, T^*[2](\gg / \gg))$.  This equivalence is $\mr U(1)$-invariant.
\end{theorem}
